---
title: "Data Science HW-5"
author: "Kasturi Bhamidipati"
date: "2022-11-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
library(patchwork)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1


# Problem 2

## Importing the data

First we want to import the data. 

```{r import data}
homicide_raw = 
  read_csv(file = "./data/homicide-data.csv")
```

## Summary of the dataset 

`r skimr::skim(homicide_raw)`
- The `homicide` dataset has `r nrow(homicide_raw)` rows and `r ncol(homicide_raw)` columns. 
- It has the following variables: `r colnames(homicide_raw)`
- It provides details on the date of the homicide, the victims' name, age, sex, city and state. 
- It also had additional notes on the status of the case. 

## Creating `city_state` variable and summarizing

```{r city_state}
homicide_data = 
  homicide_raw%>%
  unite("city_state", city:state, remove = FALSE, sep=", ") %>%
  group_by(city_state) %>%
  count(disposition, name = "total_dispositions")%>%
  pivot_wider(
    names_from= "disposition",
    values_from= "total_dispositions"
    )%>%
  janitor::clean_names()%>% 
  replace(is.na(.), 0)%>%
  mutate(
    total_homicides = closed_by_arrest+closed_without_arrest+open_no_arrest, 
    unsolved_homicides = closed_without_arrest+open_no_arrest
  )
  
```

